---
title: "Hormones"
output:
  html_document: 
    highlight: tango
    theme: paper
    fig_width: 10
  pdf_document: default
  word_document: default
date: "2023-07-18"
editor_options:
  chunk_output_type: inline
---

# Set-Up

## Loading Packages

```{r install packages, warning=F, include=F}
env <- new.env() # Create a new environment
source("Scripts/RPackages/packages.R", local = env) # Load the packages into the new environment

loaded_packages <- ls(envir = env) # Get the list of loaded packages in the new environment

invisible(lapply(loaded_packages, function(pkg) { # Load the packages that are not already loaded into the global environment
  if (!(pkg %in% search())) {
    library(pkg, character.only = TRUE)
  }
}))
```

## Loading DF
```{r}
A.Hormones <- read_excel(path= "Data/hormones/DF_Hormones.xlsx") #session 1 to 4

hormones_families <- read_excel(path= "Data/hormones/DF_Hormones_Families.xlsx")

hormones_desnsesampling <- read_excel(path= "Data/hormones/DF_Hormones_DenseSampling.xlsx")
```

```{r}
A.Hormones$Group <- factor(A.Hormones$Group, levels = c("nulliparous_women", "gestational_mother", "non_gestational_mother"))
```

# Checking Steroid Hormones Trajectory during pregnancy and postpartum =========

```{r base table with mean and sd per session}
meanHormones_session <- A.Hormones %>%  
  filter(Group == "gestational_mother") %>% 
  select(Session,log_Cortisol_F_corrected:log_E1_G_corrected) %>%
  tbl_summary(by=Session,statistic = list(all_continuous() ~ "{mean} ({sd})"), digits=all_continuous() ~ 2)

meanHormones_session <- as.data.frame(meanHormones_session)
  
colnames(meanHormones_session) <- c("Hormone","Horm. Concentration (Baseline)", "Horm. Concentration (18 prg. weeks)", "Horm. Concentration (32 prg. weeks)","Horm. Concentration (1 month postpartum)")
```

```{r building the models}
A.Hormones$Session <- as.numeric(A.Hormones$Session)

loghormones <- colnames(A.Hormones[, grepl("log.*corrected", colnames(A.Hormones))]) #selecting hormones (log and creatinine corrected)

#QUADRATIC MODEL ===============================================================
summary_list_quadratic <- list()

for (i in 1:length(loghormones)) {
  formula_str <- paste(loghormones[i], "~ poly(Session, 2) * Group + BMI_sc + Age_sc + Diftime_sc + (1 | Identity)")
  model <- lmer(data = A.Hormones, formula = as.formula(formula_str))
  summary_list_quadratic[[loghormones[i]]] <- summary(model)
}

#LINEAR MODEL ==================================================================
summary_list_linear <- list()

for (i in 1:length(loghormones)) {
  formula_str <- paste(loghormones[i], "~ Session * Group + BMI_sc + Age_sc + Diftime_sc + (1 | Identity)")
  model <- lmer(data = A.Hormones, formula = as.formula(formula_str))
  summary_list_linear[[loghormones[i]]] <- summary(model)
}

hormones_families_1 <- hormones_families %>%
  mutate(Hormone = paste0("log_",Hormone,"_corrected"))
```
## Quadratic Trajectory (Gest Mothers group)

```{r gestational_mother quad}
significant_loghormones <- c()
non_significant_loghormones <- c()
trajectory_df_GMq <- data.frame(Hormone=character(), pvalue= numeric(), stringsAsFactors = F)


for (i in 1:length(loghormones)) {
  interaction_p_value <- summary_list_quadratic[[loghormones[i]]]$coefficients["poly(Session, 2)2:Groupgestational_mother","Pr(>|t|)"]
  interaction_estimate <- summary_list_quadratic[[loghormones[i]]]$coefficients["poly(Session, 2)2:Groupgestational_mother","Estimate"]
  trajectory_df_GMq <- rbind(trajectory_df_GMq, data.frame(Hormone = loghormones[i], pvalue = interaction_p_value, Estimate= interaction_estimate))
}

trajectory_df_GMq <- merge(trajectory_df_GMq,hormones_families_1, by="Hormone",all=T)
trajectory_df_GMq$SteroidFamily <- factor(trajectory_df_GMq$SteroidFamily, levels = c("ESTROGENS","PROGESTOGENS","CORTICOIDS","ANDROGENS"),ordered=T)

trajectory_df_GMq_1 <- merge(trajectory_df_GMq,meanHormones_session,by="Hormone")

trajectory_df_GMq_1 <- trajectory_df_GMq_1 %>%
  group_by(SteroidFamily) %>%
  mutate(Significance_FDR = p.adjust(pvalue,method="fdr")) %>%
  ungroup() %>%
  select(SteroidFamily,Compound,`Horm. Concentration (Baseline)`:`Horm. Concentration (1 month postpartum)`,Estimate,pvalue, Significance_FDR)

trajectory_df_GMq_1 <- trajectory_df_GMq_1 %>%
  mutate(Significance = ifelse(Significance_FDR < 0.001, "***",
                    ifelse(Significance_FDR  < 0.01, "**",
                    ifelse(Significance_FDR  < 0.05, "*", "ns"))))

colnames(trajectory_df_GMq_1) <- c("Steroid Family","Metabolite", "Horm. Concentration (Baseline)", "Horm. Concentration (18 prg. weeks)","Horm. Concentration (32 prg. weeks)", "Horm. Concentration (1 month postpartum)", "Est.", "p value" , "q value", "Sig.")

custom_round <- function(x, column_name) {
  if (grepl("p value|q value", column_name)) {
    return(ifelse(x < 0.001, format(x, scientific = TRUE, digits = 3), format(round(x, 3))))
  }
  if (is.numeric(x) & !grepl("p value|q value", column_name)) {
    return(ifelse(x < 0.005 & x > -0.005, format(round(x, 3)), format(round(x, 2))))
  }
  return(x)
}
trajectory_df_GMq_1 <- trajectory_df_GMq_1 %>% arrange(`Steroid Family`,`q value`)
trajectory_df_GMq_1 <- trajectory_df_GMq_1 %>% 
  mutate(across(everything(), ~custom_round(.x, cur_column())))

trajectory_df_GMq_1fin <- as_grouped_data(trajectory_df_GMq_1,"Steroid Family")

trajectory_df_GMq_1fin %>% regulartable()
```

# Multimodal Analysis ==========================================================

```{r merging brain and A.Hormones df, include = F}
A.Hormones_GM <- A.Hormones %>% filter(Group == "gestational_mother")
```

## Correlation between quadratic trajectories

### cortical gray matter volume model

```{r}
gmv_lmer <- lmer(PChange.Cortvol.Global ~ poly(Session,2) + (poly(Session,2)|Identity), data=A.Hormones_GM)

rancoef_gmv <- (ranef(gmv_lmer)$Identity) #*-1 #random coefficient gmv
```

### Hormonal models

```{r}
trajectory_df_GMq_plot <- trajectory_df_GMq %>%
  group_by(SteroidFamily) %>%
  mutate(Significance_FDR = p.adjust(pvalue,method="fdr")) %>%
  ungroup() %>%
  mutate(Trajectory = ifelse(Significance_FDR < 0.05,"quadratic","ns"),
         Curve = ifelse(Significance_FDR > 0.05, NA, ifelse(Estimate > 0, "U-Shape", "Inverse U-Shape")))  %>%
  #filter(Trajectory=="quadratic") %>%
  select(Hormone, Compound,SteroidFamily, Trajectory,Significance_FDR) %>%
  mutate(SteroidFamily= factor(SteroidFamily,levels = c("ESTROGENS","PROGESTOGENS","CORTICOIDS","ANDROGENS"))) %>%
  mutate(Compound = ifelse(Trajectory == "quadratic",paste0(Compound," *"), Compound))%>%
  arrange(SteroidFamily,Significance_FDR)
```

#### Estrogens

```{r}
estrogens <- trajectory_df_GMq_plot %>%
  filter(SteroidFamily == "ESTROGENS") %>%
  filter(Trajectory == "quadratic")

model_summaries <- list()
estrogen_cortest <- data.frame(Hormone= character(), pvalue_unc=numeric(), estimate=numeric(), stringsAsFactors = F)

for (i in 1:length(estrogens$Hormone)) {
  estrogen <- estrogens$Hormone[i]
  formula <- as.formula(paste(estrogen, "~ poly(Session,2) + (poly(Session,2) | Identity)"))  
  hormones_lmer <- lmer(formula, data=A.Hormones_GM)
  model_summaries[[estrogen]] <- summary(hormones_lmer)
  
  rancoef_hormones <- ranef(hormones_lmer)$Identity #random coefficient hormones
  cortest <- cor.test(rancoef_gmv$`poly(Session, 2)2`, rancoef_hormones$`poly(Session, 2)2`, method = "spearman",alternative="two.sided") #significant
  estrogen_cortest <- rbind(estrogen_cortest, data.frame(Hormone = estrogen, pvalue_unc = cortest$p.value, estimate = cortest$estimate))
}

estrogen_cortest <- estrogen_cortest %>% mutate(pvalue_FDR = p.adjust(pvalue_unc,method="fdr"),
                                                Significance = ifelse(pvalue_FDR < 0.001, "***",
                                                                      ifelse(pvalue_FDR  < 0.01, "**",
                                                                             ifelse(pvalue_FDR  < 0.05, "*", "ns")))) %>%
                      arrange(pvalue_FDR)%>%
                      add_column(`Steroid Family` = "Estrogens")
estrogen_cortest
```

#### Progestagens

```{r}
progestogens <- trajectory_df_GMq_plot %>%
  filter(SteroidFamily == "PROGESTOGENS") %>%
  filter(Trajectory == "quadratic")

progestogen_cortest <- data.frame(Hormone= character(), pvalue_unc=numeric(), estimate=numeric(), stringsAsFactors = F)

for (i in 1:length(progestogens$Hormone)) {
  progestogen <- progestogens$Hormone[i]
  formula <- as.formula(paste(progestogen, "~ poly(Session,2) + (poly(Session,2) | Identity)"))  
  hormones_lmer <- lmer(formula, data=A.Hormones_GM)
  
  rancoef_hormones <- ranef(hormones_lmer)$Identity #random coefficient hormones
  cortest <- cor.test(rancoef_gmv$`poly(Session, 2)2`, rancoef_hormones$`poly(Session, 2)2`, method = "spearman",alternative="two.sided") #significant
  progestogen_cortest <- rbind(progestogen_cortest, data.frame(Hormone = progestogen, pvalue_unc = cortest$p.value, estimate = cortest$estimate))
}

progestogen_cortest <- progestogen_cortest %>% mutate(pvalue_FDR = p.adjust(pvalue_unc,method="fdr"),
                                                Significance = ifelse(pvalue_FDR < 0.001, "***",
                                                                      ifelse(pvalue_FDR  < 0.01, "**",
                                                                             ifelse(pvalue_FDR  < 0.05, "*", "ns")))) %>%
  arrange(pvalue_FDR) %>%
  add_column(`Steroid Family` = "Progestogens")

if (any(!is.na(progestogen_cortest$significance))) {
  print(progestogen_cortest)
  } else {
  print("No significant correlations")
    }
```

#### Corticoids

```{r}
corticoids <- trajectory_df_GMq_plot %>%
  filter(SteroidFamily == "CORTICOIDS") %>%
  filter(Trajectory == "quadratic")

corticoid_cortest <- data.frame(Hormone= character(), pvalue_unc=numeric(), estimate=numeric(), stringsAsFactors = F)

for (i in 1:length(corticoids$Hormone)) {
  corticoid <- corticoids$Hormone[i]
  formula <- as.formula(paste(corticoid, "~ poly(Session,2) + (poly(Session,2) | Identity)"))  
  hormones_lmer <- lmer(formula, data=A.Hormones_GM)
  
  rancoef_hormones <- ranef(hormones_lmer)$Identity #random coefficient hormones
  cortest <- cor.test(rancoef_gmv$`poly(Session, 2)2`, rancoef_hormones$`poly(Session, 2)2`, method = "spearman",alternative="two.sided") #significant
  corticoid_cortest <- rbind(corticoid_cortest, data.frame(Hormone = corticoid, pvalue_unc = cortest$p.value, estimate = cortest$estimate))
}

corticoid_cortest <- corticoid_cortest %>% mutate(pvalue_FDR = p.adjust(pvalue_unc,method="fdr"),
                                                Significance = ifelse(pvalue_FDR < 0.001, "***",
                                                                      ifelse(pvalue_FDR  < 0.01, "**",
                                                                             ifelse(pvalue_FDR  < 0.05, "*", "ns")))) %>%
  arrange(pvalue_FDR) %>%
  add_column(`Steroid Family` = "Corticoids")

if (any(!is.na(corticoid_cortest$significance))) {
  print(corticoid_cortest)
  } else {
  print("No significant correlations")
    }
```

#### Androgens

```{r}
androgens <- trajectory_df_GMq_plot %>%
  filter(SteroidFamily == "ANDROGENS") %>%
  filter(Trajectory == "quadratic")

androgen_cortest <- data.frame(Hormone= character(), pvalue_unc=numeric(), estimate=numeric(), stringsAsFactors = F)

for (i in 1:length(androgens$Hormone)) {
  androgen <- androgens$Hormone[i]
  formula <- as.formula(paste(androgen, "~ poly(Session,2) + (poly(Session,2) | Identity)"))  
  hormones_lmer <- lmer(formula, data=A.Hormones_GM)
  
  rancoef_hormones <- ranef(hormones_lmer)$Identity #random coefficient hormones
  cortest <- cor.test(rancoef_gmv$`poly(Session, 2)2`, rancoef_hormones$`poly(Session, 2)2`, method = "spearman",alternative="two.sided") #significant
  androgen_cortest <- rbind(androgen_cortest, data.frame(Hormone = androgen, pvalue_unc = cortest$p.value, estimate = cortest$estimate))
}

androgen_cortest <- androgen_cortest %>% mutate(pvalue_FDR = p.adjust(pvalue_unc,method="fdr"),
                                                Significance = ifelse(pvalue_FDR < 0.001, "***",
                                                                      ifelse(pvalue_FDR  < 0.01, "**",
                                                                             ifelse(pvalue_FDR  < 0.05, "*", "ns")))) %>%
  arrange(pvalue_FDR) %>%
  add_column(`Steroid Family` = "Androgens")

if (any(!is.na(androgen_cortest$significance))) {
  print(androgen_cortest)
  } else {
  print("No significant correlations")
    }
```

## Results table

```{r}
hormonal_correlations <- rbind(estrogen_cortest,progestogen_cortest,corticoid_cortest,androgen_cortest)

hormonal_correlations$`Steroid Family` <- factor(hormonal_correlations$`Steroid Family`, levels = c("Estrogens","Progestogens","Corticoids","Androgens"),ordered=T)

hormonal_correlations <- merge(hormonal_correlations,hormones_families_1 %>% select(Hormone,Compound), by="Hormone") %>%
  select(`Steroid Family`,Compound, estimate, pvalue_unc, pvalue_FDR, Significance) %>% arrange(`Steroid Family`,pvalue_FDR)

colnames(hormonal_correlations) <- c("Steroid Family", "Compound", "Correlation Coefficient","p value", "q value","Sig.")

custom_round <- function(x) {
  if (grepl("value", cur_column())) {
    return(ifelse(x < 0.001,format(x, scientific = TRUE, digits = 3), format(round(x, 3))))
  }
  if (is.numeric(x)) {
    return(round(x, 2))
  }
  return(x)
}

# EXPORT TABLE
hormonal_correlations <- hormonal_correlations %>% 
  mutate(across(everything(), custom_round))

hormonal_correlations_table <- as_grouped_data(hormonal_correlations,"Steroid Family")
hormonal_correlations_table %>% regulartable() %>% autofit()
```

# Figures ========================================================================

## Boxplots (Supplementary figures S6 to S9)

```{r first visualization log transformed, fig.height=15, fig.width=20}
A.Hormones$Session1 <- c(-1, 18, 34, 43)[match(A.Hormones$Session, c(1, 2, 3, 4))] #adjust to real means
custom_labels <- c("Baseline","18 PW","34 PW", "1 MPP")
custom_braks <- c(-1, 18, 34, 43, 63)

loghormones <- trajectory_df_GMq_plot
loghormones_h <- loghormones$Hormone

# A.Hormones$Session <- as.factor(A.Hormones$Session1)

ggplot_list <- lapply(loghormones_h, function(variable_name) {
  compound_name <- loghormones$Compound[loghormones$Hormone == variable_name]
  steroid_family <- loghormones$SteroidFamily[loghormones$Hormone == variable_name]
  
  # Define colors based on steroid_family
  fill_color <- case_when(
    steroid_family == "ANDROGENS" ~ "#F8766D",
    steroid_family == "ESTROGENS" ~ "#7CAE00",
    steroid_family == "PROGESTOGENS" ~ "#00BFC4",
    steroid_family == "CORTICOIDS" ~ "#C77CFF")
  line_color <- case_when(
    steroid_family == "ANDROGENS" ~ "#F8766D",
    steroid_family == "ESTROGENS" ~ "#7CAE00",
    steroid_family == "PROGESTOGENS" ~ "#00BFC4",
    steroid_family == "CORTICOIDS" ~ "#C77CFF") 
  
    A.Hormones %>%
    filter(Group=="gestational_mother")%>%
    ggplot(aes(x = Session1, y = .data[[variable_name]], color = Group)) + #fill = Group
    geom_rect(aes(xmin = 0, xmax = 40, ymin = -Inf, ymax = Inf), fill = "gray80", color = "white", alpha = 0.01) +
    geom_jitter(size = 2, alpha = 0.2) +
    stat_summary(geom = "errorbar", fun.data = mean_cl_normal, width = 0.2, size = 1.2) +
    stat_summary(geom = "line", fun.data = mean_cl_normal, size = 1.2, lineend = "round", alpha = 0.7) +
    stat_summary(geom = "point", fun.data = mean_cl_normal, size = 2, alpha = 1) +
  # scale_fill_brewer(palette = "Set2", labels = c("Nulliparous Women", "Gestational Mothers", "Non Gestational Mothers")) +
  # scale_color_brewer(palette = "Set2",labels = c("Nulliparous Women", "Gestational Mothers", "Non Gestational Mothers")) +
    scale_fill_manual(values = fill_color) +
    scale_color_manual(values = line_color) +
    scale_x_continuous(breaks = c(-1, 18, 36, 44), labels = custom_labels) +
    labs(title = compound_name,) +  # Set the title to the variable name
    theme_minimal() +
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
    theme(axis.line = element_line(size = 0.5, color = "black")) +
    theme(axis.title.x = element_blank(), legend.title = element_blank()) +
    theme(axis.text=element_text(size=15))+
    theme(axis.title.y=element_text(size=15),
          plot.title = element_text(size=15))+
    theme(legend.position ="none")+
    ylab("Logarithmic Concentration (ng/mL)")+
    guides(color=F)
})

combined_plot_1 <- ggarrange(plotlist = ggplot_list[1:6], nrow=2, ncol=3, common.legend=T,legend=NULL)
combined_plot_1
combined_plot_2 <- ggarrange(plotlist = ggplot_list[7:18], nrow=4, ncol=3, common.legend=T,legend=NULL)
combined_plot_2
combined_plot_3 <- ggarrange(plotlist = ggplot_list[19:37], nrow=5, ncol=4, common.legend=T,legend=NULL)
combined_plot_3
combined_plot_4 <- ggarrange(plotlist = ggplot_list[38:49], nrow=4, ncol=3, common.legend=T,legend=NULL)
combined_plot_4
```

## Brain-Hormone correlation plots

```{r Fig 3B left}
#fig.height=8, fig.width=9
gmv_lmer <- lmer(PChange.Cortvol.Global ~ poly(Session,2) + (poly(Session,2)|Identity), data=A.Hormones_GM)
rancoef_gmv <- (ranef(gmv_lmer)$Identity) #random coefficient gmv

hormones_lmerE33S <- lmer(log_E3_3S_corrected ~ poly(Session, 2) + (poly(Session, 2) | Identity), data=A.Hormones_GM)
rancoef_hormones_E33S <- ranef(hormones_lmerE33S)$Identity #random coefficient hormones

a <- as.data.frame(cbind(rancoef_gmv$`poly(Session, 2)2`, rancoef_hormones_E33S$`poly(Session, 2)2`))

colnames(a) <- c("GMV_QCoef","E3_3S_QCoef")


ggplo1 <- ggplot(a, aes(E3_3S_QCoef,GMV_QCoef)) +
  geom_point(size=1.5, alpha=0.9) +
  geom_smooth(method='lm',color="#99cc33") +
  ylab("% GM volume change (quadratic parameter coefficient)") +
  xlab("Estriol 3-sulfate (quadratic parameter coefficient)")+
  theme_modern()+
  theme(axis.title.y = element_text(size=7)) +
  theme(axis.title.x = element_text(size=7)) +
  theme(axis.text=element_text(size=7))+
  theme(axis.ticks = element_line())
ggplo1
```

```{r Fig 3B right}
#fig.height=7, fig.width=9
hormones_lmerE1S <- lmer(log_E1_S_corrected ~ poly(Session, 2) + (poly(Session, 2) | Identity), data=A.Hormones_GM)
rancoef_hormones_E1S <- ranef(hormones_lmerE1S)$Identity #random coefficient hormones

a <- as.data.frame(cbind(rancoef_gmv$`poly(Session, 2)2`, rancoef_hormones_E1S$`poly(Session, 2)2`))
colnames(a) <- c("GMV_QCoef","E1_S_QCoef")


ggplo2 <- ggplot(a, aes(E1_S_QCoef,GMV_QCoef)) +
  geom_point(size=1.5, alpha=0.9) +
  geom_smooth(method='lm',color="#009933")+
  ylab("% GM volume change (quadratic parameter coefficient)") +
  xlab("Estrone sulfate (quadratic parameter coefficient)")+
  theme_modern()+
  theme(axis.title.y = element_text(size=7)) +
  theme(axis.title.x = element_text(size=7)) +
  theme(axis.text=element_text(size=7))+
  theme(axis.ticks = element_line())
ggplo2
```

```{r}
A.Hormones_GM$Session1 <- c(-1, 18, 34, 43)[match(A.Hormones_GM$Session, c(1, 2, 3, 4))] #adjust to real means
filtered_data <- A.Hormones_GM[A.Hormones_GM$Session1 %in% c(18, 34, 43), ]
custom_labels <- c("Pre-Pregnancy","18 pregnancy\nweeks","34 pregnancy\nweeks", "1 month\npostpartum","6 months\npostpartum")
custom_braks <- c(-1, 18, 34, 43)
```


```{r Calculating % relative to the maximum value}
A.Hormones_GM <- A.Hormones_GM %>%
  group_by(Identity) %>%
  mutate(E3_3S_corrected_LowestValue = min(log_E3_3S_corrected), E3_3S_corrected_HighestValue = max(log_E3_3S_corrected)) %>%
  mutate(E3_3S_corrected_Percentage_Change = ((log_E3_3S_corrected-E3_3S_corrected_LowestValue)/(E3_3S_corrected_HighestValue-E3_3S_corrected_LowestValue))* 100) %>%
  mutate(E1_S_corrected_LowestValue = min(log_E1_S_corrected), E1_S_corrected_HighestValue = max(log_E1_S_corrected)) %>%
  mutate(E1_S_corrected_Percentage_Change = ((log_E1_S_corrected-E1_S_corrected_LowestValue)/(E1_S_corrected_HighestValue-E1_S_corrected_LowestValue))* 100)
```

```{r Fig 3A}
coef <-  10
coef1 <- 2

FIg3A <- ggplot(data = A.Hormones_GM, aes(x = Session1)) +
  geom_rect(aes(xmin = 0, xmax = 40, ymin = -Inf, ymax = Inf), fill = "gray80", color = "white", alpha = 0.01) +
  stat_summary(aes(y=PChange.Cortvol.Global*coef1, color="GM Volume"), geom = "line", fun.data = mean_cl_normal, linejoin = "round", size = 1.2, alpha = 0.7) +
  stat_summary(aes(y=PChange.Cortvol.Global*coef1,color="GM Volume"), geom = "errorbar", fun.data = mean_cl_normal, width = 1.2, size = 1.2, alpha = 0.7) +
  stat_summary(aes(y=PChange.Cortvol.Global*coef1), geom = "point", fun.data = mean_cl_normal, size = 2, alpha = 1,ccolor="black") +
  stat_summary(aes(y=E3_3S_corrected_Percentage_Change/coef,color="estriol 3-sulfate"),geom = "line", fun.data = mean_cl_normal, size = 1.2, linejoin = "round", alpha = 0.7) +
  stat_summary(aes(y=E3_3S_corrected_Percentage_Change/coef,color="estriol 3-sulfate"),geom = "errorbar", fun.data = mean_cl_normal, width = 1.2, size = 1.2, alpha = 0.7) +
  stat_summary(aes(y=E3_3S_corrected_Percentage_Change/coef,color="estriol 3-sulfate"),geom = "point", fun.data = mean_cl_normal, size = 2, alpha = 1 ,color="black") +
  stat_summary(aes(y=E1_S_corrected_Percentage_Change/coef,color="estrone sulfate"),geom = "line", fun.data = mean_cl_normal, size = 1.2, linejoin = "round", alpha = 0.7) +
  stat_summary(aes(y=E1_S_corrected_Percentage_Change/coef,color="estrone sulfate"),geom = "errorbar", fun.data = mean_cl_normal, width = 1.2, size = 1.2, alpha = 0.7) +
  stat_summary(aes(y=E1_S_corrected_Percentage_Change/coef,color="estrone sulfate"),geom = "point", fun.data = mean_cl_normal, size = 2, alpha = 1,color="black") +
  scale_y_continuous(name="% Change in Gray Matter Volume", labels = c("-10" = "-5", "-5" = "-2.5", "0" = "0","5" = "", "10" = ""),
                     sec.axis=sec_axis(~.*coef,name="Relative levels of Estrogens (% of max)", labels=c("-100" = "", "-50" = "", "0" = " min (0%)","50" = "50%", "100" = "max (100%)")))+
  scale_x_continuous(breaks = c(-1, 18, 36, 44, 64), labels = custom_labels) +
  scale_color_manual(name="",values = c("GM Volume" = "coral","estriol 3-sulfate"="#99cc33","estrone sulfate" = "#009933"))+
  theme_minimal() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  theme(axis.line = element_line(size = 0.5, color = "black")) +
  theme(axis.title.x = element_blank()) +
  theme(axis.title.y = element_text(colour = "coral")) +  # Set primary y-axis color to coral
  theme(axis.title.y.right = element_text(colour = "#339933")) +  # Set secondary y-axis color to aquamarine2
  theme(legend.position = "bottom",legend.text=element_text(size=7)) +
  theme(axis.ticks.x = element_line()) +
  theme(axis.title.y = element_text(size=7)) +
  theme(axis.text=element_text(size=7))
  

FIg3A

```
## Correspondance with dense sampling hormonal acquisitions

```{r}
hormones_general <- A.Hormones_GM %>% mutate(Session = case_when(Session=="1" ~ "0", Session=="2" ~ "18", Session=="3" ~ "34", Session=="4" ~ "43"))
```

```{r}
hormones_desnsesampling$Pregnancy_Week <- as.numeric(hormones_desnsesampling$Pregnancy_Week)
hormones_general$Session <- as.numeric(hormones_general$Session)

e1s_ds <- ggplot() +
  geom_rect(aes(xmin = 3, xmax = 40, ymin = -Inf, ymax = Inf), fill = "gray80", color = "white", alpha = 0.1) +
    stat_summary(data=hormones_desnsesampling, aes(x=Pregnancy_Week, y = log_E1_S_corrected), geom = "errorbar", fun.data = mean_cl_normal, width = 0.2, size = 1.2, color = "#cccccc") +
    stat_summary(data=hormones_desnsesampling, aes(x=Pregnancy_Week, y = log_E1_S_corrected), geom = "line", fun.data = mean_cl_normal, size = 1.2, lineend = "round", alpha = 0.7, group=1, color = "#cccccc") +
    stat_summary(data=hormones_desnsesampling, aes(x=Pregnancy_Week, y = log_E1_S_corrected), geom = "point", fun.data = mean_cl_normal, size = 2, alpha = 1, color = "#333333") +
      geom_jitter(data=hormones_desnsesampling, aes(x=Pregnancy_Week, y = log_E1_S_corrected), width = 0.2, height = 0.2, size = 2, alpha = 0.7, color = "#666666") +
    geom_jitter(data=hormones_general, aes(x=Session, y = log_E1_S_corrected), width = 0.3, height = 0.2, size = 2, alpha = 0.2, color = "#009933") +
    stat_summary(data=hormones_general, aes(x=Session, y = log_E1_S_corrected), geom = "errorbar", fun.data = mean_cl_normal, width = 0.2, size = 1.2, color = "#009933") +
    stat_summary(data=hormones_general, aes(x=Session, y = log_E1_S_corrected), geom = "line", fun.data = mean_cl_normal, size = 1.2, lineend = "round", alpha = 0.7, group=1, color = "#009933") +
    stat_summary(data=hormones_general, aes(x=Session, y = log_E1_S_corrected), geom = "point", fun.data = mean_cl_normal, size = 2, alpha = 1, color = "#333333") +
    theme_minimal() +
    labs(title = "Estrone sulfate") + 
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
    theme(axis.line = element_line(size = 0.5, color = "black")) +
    theme(legend.title = element_blank()) +
    theme(axis.text=element_text(size=7)) +
    theme(axis.title.y=element_text(size=7),
          axis.title.x=element_blank(),
          plot.title = element_text(size=7)) +
  theme(axis.ticks = element_line())+
    theme(legend.position ="none") +
    ylab("Logarithmic Concentration (ng/mL)") +
  scale_x_continuous(breaks=c(0,10,12,14,16,18,20,22,24,26,28,30,32,34,36,38,30,42,44))+
    guides(color=F) +
    scale_color_manual(values = c("#cccccc", "#009933"))

e1s_ds
```

```{r}
e33s_ds <- ggplot() +
  geom_rect(aes(xmin = 3, xmax = 40, ymin = -Inf, ymax = Inf), fill = "gray80", color = "white", alpha = 0.1) +
    stat_summary(data=hormones_desnsesampling, aes(x=Pregnancy_Week, y = log_E3_3S_corrected), geom = "errorbar", fun.data = mean_cl_normal, width = 0.2, size = 1.2, color = "#cccccc") +
    stat_summary(data=hormones_desnsesampling, aes(x=Pregnancy_Week, y = log_E3_3S_corrected), geom = "line", fun.data = mean_cl_normal, size = 1.2, lineend = "round", alpha = 0.7, group=1, color = "#cccccc") +
    stat_summary(data=hormones_desnsesampling, aes(x=Pregnancy_Week, y = log_E3_3S_corrected), geom = "point", fun.data = mean_cl_normal, size = 2, alpha = 1, color = "#333333") +
      geom_jitter(data=hormones_desnsesampling, aes(x=Pregnancy_Week, y = log_E3_3S_corrected), width = 0.2, height = 0.2, size = 2, alpha = 0.7, color = "#666666") +
    geom_jitter(data=hormones_general, aes(x=Session, y = log_E3_3S_corrected), width = 0.3, height = 0.2, size = 2, alpha = 0.2, color = "#99cc33") +
    stat_summary(data=hormones_general, aes(x=Session, y = log_E3_3S_corrected), geom = "errorbar", fun.data = mean_cl_normal, width = 0.2, size = 1.2, color = "#99cc33") +
    stat_summary(data=hormones_general, aes(x=Session, y = log_E3_3S_corrected), geom = "line", fun.data = mean_cl_normal, size = 1.2, lineend = "round", alpha = 0.7, group=1, color = "#99cc33") +
    stat_summary(data=hormones_general, aes(x=Session, y = log_E3_3S_corrected), geom = "point", fun.data = mean_cl_normal, size = 2, alpha = 1, color = "#333333") +
    theme_minimal() +
    labs(title = "Estriol 3-sulfate") + 
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
    theme(axis.line = element_line(size = 0.5, color = "black")) +
    theme(legend.title = element_blank()) +
    theme(axis.text=element_text(size=7)) +
    theme(axis.title.y=element_text(size=7),
          axis.title.x=element_blank(),
          plot.title = element_text(size=7)) +
  theme(axis.ticks = element_line())+
    theme(legend.position ="none") +
    ylab("Logarithmic Concentration (ng/mL)") +
  scale_x_continuous(breaks=c(0,10,12,14,16,18,20,22,24,26,28,30,32,34,36,38,30,42,44))+
    guides(color=F) +
    scale_color_manual(values = c("#cccccc", "#99cc33"))
e33s_ds

```

